### 2017-11-28 paper/sections/5_file-systems.tex
paper: update author list, addresses #51
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

  \item Scheduling: when to yield computation cycles to another process, how
much of a resource to allocate. We could use Mantle to implement something like the RBED
scheduler~\cite{brandt:rtss2003-rad}, that separates resource allocation from
timing of delivery to enable real-time and non-real-time-scheduling classes.

  \item Batching: how many operations to group together and when to send large
batches of updates. We could use Mantle to shape the batching policies in the
shared resource interface in  Malacology~\cite{sevilla:eurosys17-malacology}.

  \item Prefetching: how much to prefetch and how to select data to retrieve.
We could use Mantle to implement forward/backward/stride detection algorithms
for prefetching in RAID arrays or something more complicated, like the time
series algorithms for adaptive I/O prefetching presented
in~\cite{tran:sc01-arima}.

>>>>

  \item Scheduling: when to yield computation cycles to another process, how
much of a resource to allocate. We could use Mantle to implement the
fairness/priority models used in the Mesos~\cite{hindman_mesos_2011} ``how
many" policies.

  \item Batching: how many operations to group together, when to send large
batches of updates. We could use Mantle to implement to the pathname leases from
IndexFS~\cite{ren:sc2014-indexfs} or the capabilities from
CephFS\footnote{http://docs.ceph.com/docs/master/cephfs/capabilities/}.

  \item Prefetching: how much to prefetch, how to select data.  We could use
Mantle to implement forward/backward/stride detection algorithms for
prefetching in RAID arrays or something more complicated, like the time series
algorithms for adaptive I/O prefetching from~\cite{tran:sc01-arima}.
